Gafo-cc-analysis

### 2024-01-03 analysis/gafo-cc-analysis.Rmd
add model for cluster run

library(tidyverse)
library(tidybayes)
library(ggthemes)
library(brms)
```

```{r}
mdata <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  ungroup()%>%
  mutate(ageinyears = scale(ageinyears),
         targetcentralityx = scale(targetcentralityx),
         trialnr = scale(trialnr),
         #children = scale(children),
         #household = scale(household),
         #younger_children = scale(younger_children),
         touchscreen = factor(touchscreen),
        screen = factor(screen),
        click = abs(clickdistfromtargetcenterx))%>%
  #filter(community != "chimfunshi")%>%
  select(subjid,community,ageinyears,children, household, younger_children,trialnr, screen,touchscreen, targetcentralityx, click )

@@

bm_octs_rand <- brm(mean_click ~ ageinyears + touchscreen + older_children + (ageinyears + older_children |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             #backend = "cmdstanr"
             )%>%
  add_criterion(., c("waic","loo"))

@@

model_weights(bm_base,
            #bm_full_fix, 
            bm_full_rand,
            bm_fullc_fix,
            #bm_cts_fix,
            #bm_ycts_fix,
            bm_octs_fix,
            bm_octs_fix_int,
            bm_octs_rand_int,
            bm_octs_rand,
            #bm_full_rand
            #bm_hhts_fix#,
            #bm_cts_fix_int,
            #bm_cts_rand_int,
            #bm_cts_rand#,
            #bm_hhts_rand_2, 
            #bm_hhts_rand,
            criterion = "loo")%>%as_tibble(rownames = "model")

fixef(bm_cts_rand)
```
```{r}
ndata <- scdata%>%
  distinct(community, ageinyears)

@@

```{r}
as_draws_df(bm_cts_rand_int)%>%
  select(contains("children"))%>%
  select(contains("children"))%>%
  pivot_longer(cols = contains("children]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_children, 
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",children"))%>%
  ggplot(aes(x= post, y = community))+
  stat_slabinterval()+
  xlim(-0.15, 0.1)+
  theme_bw()
```

@@

>>>>

library(tidyverse)
library(tidybayes)
library(ggthemes)
library(brms)
library(ggridges)
```

```{r}
mdata <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  ungroup()%>%
  mutate(older_children = children - 1 - younger_children)%>%
  mutate(ageinyears = scale(ageinyears),
         targetcentralityx = scale(targetcentralityx),
         trialnr = scale(trialnr),
         touchscreen = factor(touchscreen),
        screen = factor(screen),
        click = abs(clickdistfromtargetcenterx))%>%
  group_by(community)%>%
  mutate(children = scale(children),
         household = scale(household),
         younger_children = scale(younger_children),
         older_children = scale(older_children))%>%
  select(subjid,community,ageinyears,children, household, younger_children,older_children, trialnr, screen,touchscreen, targetcentralityx, click )

@@

bm_octs_rand <- brm(mean_click ~ ageinyears + touchscreen + older_children + (ageinyears + touchscreen + older_children |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             #backend = "cmdstanr"
             )%>%
  add_criterion(., c("waic","loo"))

@@

model_weights(bm_base,
            #bm_full_fix, 
            bm_full_rand,
            bm_fullc_fix,
            #bm_cts_fix,
            #bm_ycts_fix,
            bm_octs_fix,
            #bm_octs_fix_int,
            #bm_octs_rand_int,
            bm_octs_rand,
            #bm_full_rand
            #bm_hhts_fix#,
            #bm_cts_fix_int,
            #bm_cts_rand_int,
            #bm_cts_rand#,
            #bm_hhts_rand_2, 
            #bm_hhts_rand,
            criterion = "loo")%>%as_tibble(rownames = "model")

fixef(bm_octs_rand)
```
```{r}
ndata <- scdata%>%
  distinct(community, ageinyears)

@@

```{r}
as_draws_df(bm_octs_rand)%>%
  select(contains("children"))%>%
  select(contains("children"))%>%
  pivot_longer(cols = contains("children]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_older_children, 
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",older_children]"),
         community = str_remove(community, "\\["))%>%
  ggplot(aes(x= post, y = community))+
  geom_vline(xintercept = 0, lty = 3, alpha = 0.75)+
  geom_density_ridges(rel_min_height = 0.01, col = "white", alpha = .75)+
  #stat_pointinterval()+
  #xlim(-0.15, 0.1)+
  theme_bw()

as_draws_df(bm_octs_rand)%>%
  select(contains("touchscreen"))%>%
  select(contains("touchscreen"))%>%
  pivot_longer(cols = contains("touchscreen1]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_touchscreen1, 
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",touchscreen1]"),
         community = str_remove(community, "\\["))%>%
  ggplot(aes(x= post, y = community))+
  geom_vline(xintercept = 0, lty = 3, alpha = 0.75)+
  geom_density_ridges(rel_min_height = 0.01, col = "white", alpha = .75)+
  #stat_pointinterval()+
  #xlim(-0.15, 0.1)+
  theme_bw()

as_draws_df(bm_octs_rand)%>%
  select(contains("ageinyears"))%>%
  select(contains("ageinyears"))%>%
  pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_ageinyears, 
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",ageinyears]"),
         community = str_remove(community, "\\["))%>%
  ggplot(aes(x= post, y = community))+
  geom_vline(xintercept = 0, lty = 3, alpha = 0.75)+
  geom_density_ridges(rel_min_height = 0.01, col = "white", alpha = .75)+
  #stat_pointinterval()+
  #xlim(-0.15, 0.1)+
  theme_bw()

bind_rows(
as_draws_df(bm_octs_rand)%>%
  select(contains("children"))%>%
  select(contains("children"))%>%
  pivot_longer(cols = contains("children]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_older_children, 
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",older_children]"),
         community = str_remove(community, "\\["))%>%
  select(community, post)%>%
  mutate(type = "older_children"),

as_draws_df(bm_octs_rand)%>%
  select(contains("touchscreen"))%>%
  select(contains("touchscreen"))%>%
  pivot_longer(cols = contains("touchscreen1]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_touchscreen1, 
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",touchscreen1]"),
         community = str_remove(community, "\\["))%>%
  select(community, post)%>%
  mutate(type = "touchscreen"),

as_draws_df(bm_octs_rand)%>%
  select(contains("ageinyears"))%>%
  select(contains("ageinyears"))%>%
  pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_ageinyears, 
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",ageinyears]"),
         community = str_remove(community, "\\["))%>%
  select(community, post)%>%
  mutate(type = "ageinyears")

)%>%
  ggplot(aes(x= post, y = community))+
  geom_density_ridges(rel_min_height = 0.005, col = "black", alpha = .75, fill = NA)+
  geom_vline(xintercept = 0, lty = 3)+
  facet_grid(~type, scales = "free_x")+
  #stat_pointinterval(size = 0.1)+
  #xlim(-0.15, 0.1)+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "black", fill=NA, size = .5))

@@

# Trial level analysis

```{r}
bm_trial_base <- brm(click ~ targetcentralityx + ageinyears + (targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

bm_trial_pred <- brm(click ~ targetcentralityx + ageinyears + touchscreen + older_children + (targetcentralityx|subjid)+ (ageinyears + touchscreen + older_children |community),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))
```
